### 2023-11-07 main.tex
''
^^

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. We pick the dual configuration $\xi=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
	\bm{\xi}=\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
Denoting the $m$-point correlations in the non-equilibrium steady state (NESS) by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]$ we have 
%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$). Therefore, we have the following equalities
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})
\end{split}
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
\end{equation}
 namely the joint probability of having, for all $k=1,\ldots,m$, $t_{k}$ particles of species $a_{k}$ initially positioned at site $x_{k}$ are absorbed at left and $1-t_{k}$ of the same particles absorbed at right. Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.

@@

	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})

@@

 using the binomial theorem we rewrite the \eqref{exactCorrelations} as 
		\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&

@@

		f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\right)\\

@@

		f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt
By exchanging the summations we rewrite as 
		\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
		\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\\
		=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt
%The elements of the duality matrix in this integrable case are given in equation \eqref{ElementsDualityMatrixChain_1}. Thus we have that 
%	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}D(\tau,\hat{\bm{\xi}})\langle\tau|\Psi\rangle
%where the dual configuration is $\hat{\bm{\xi}}=\sum_{k=1}^{m}\delta^{y_{k}}_{s_{k}}$. 
Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities. 

@@

	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state using $|\Psi^{'}\rangle$ of the previous step. Using duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$. However, for the sake of completeness we report it Appendix \ref{appB}. 

@@

		\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)

@@

	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{j=x_{\ell_{k}}}^{L}c_{j}\right)\dt

>>>>

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. We pick the dual configuration $\xi=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
	\bm{\xi}=\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
Denoting the $m$-point correlations in the non-equilibrium steady state (NESS) by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]$ we have 
%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$). Therefore, we have the following equalities
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
\end{split}
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
 namely the joint probability of having, for all $k=1,\ldots,m$, $t_{k}$ particles of species $a_{k}$ initially positioned at site $x_{k}$ are absorbed at left and $1-t_{k}$ of the same particles absorbed at right. Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.

@@

	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})

@@

From \eqref{exactCorrelations} we have 
		&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&

@@

		f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{k}-t_{k}}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\

@@

		f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
		\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
		=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)\dt
From first to second line we have used the binomial theorem and from third to fourth line we have changed the summation order. Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities given in \eqref{abs-probabilities}. 

@@

	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state using $|\Psi^{'}\rangle$ of the previous step. Exploiting duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$. However, for the sake of completeness we report it Appendix \ref{appB}. 

@@

		\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)

@@

	\prod_{x=1}^{L}\left(L+2-x-\sum_{j=x}^{L}c_{j}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{j=x_{\ell_{k}}}^{L}c_{j}\right)\dt
